PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Update PANNEURO_analysis_WHO_pres.Rmd
added binary case/control

```{r}
dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_case = if_else(cfs.sum_score > 11, "Fatigue", "No fatigue")) #not sure if 11 is the right cut off

>>>>

```{r}
dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_problems_with_tiredness_binary<- if_else(dat.raw$cfs.do_you_have_problems_with_tiredness_numeric >= 3, 1,0)
dat.raw$cfs.do_you_feel_sleepy_or_drowsy_binary <- if_else(dat.raw$cfs.do_you_feel_sleepy_or_drowsy_numeric >= 3, 1,0)
dat.raw$cfs.do_you_feel_weak_binary <- if_else(dat.raw$cfs.do_you_feel_weak_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_difficulty_concentrating_binary <- if_else(dat.raw$cfs.do_you_have_difficulty_concentrating_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_problems_starting_things_binary <- if_else(dat.raw$cfs.do_you_have_problems_starting_things_numeric >= 3, 1,0)
dat.raw$cfs.do_you_lack_energy_binary <- if_else(dat.raw$cfs.do_you_lack_energy_numeric >= 3, 1,0)
dat.raw$cfs.do_you_need_to_rest_more_binary <- if_else(dat.raw$cfs.do_you_need_to_rest_more_numeric >= 3, 1,0)
dat.raw$cfs.how_is_your_memory_numeric_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
dat.raw$cfs.make_slips_speaking_tongue_binary <- if_else(dat.raw$cfs.make_slips_speaking_tongue_numeric >= 3, 1,0)
dat.raw$cfs.strength_muscles_binary <- if_else(dat.raw$cfs.strength_muscles_numeric >= 3, 1,0)
```

```{r}
cfs.col.names.bi <- dat.raw %>%
  select(
    starts_with("cfs") & ends_with("binary")
  ) %>%
  colnames()
cfs.col.names.bi
```
```{r}
dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_binary =
   rowSums(select(.,cfs.col.names.bi), na.rm = F) 
   )

dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_case = if_else(cfs.sum_score_binary >= 4, "Fatigue", "No fatigue"))
